---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# graphs

Quickly generate scatter plots to examine relationships between numeric variables as part of exploratory data analysis

## Installation

You can install the development version of graphs like so:

Package installation can be performed directly by calling
`devtools::install_github("stat545ubc-2025/graphs")`


## Example

To run this example, you must first load the package using the ```library()``` function

An example data frame has been provided to showcase function usage. One can also import datasets from other packages using the form ```package::function()```

1. The ```example_data``` is used to create a scatter plot using a dataframe within the package itself

2. The ```flight_delay_example``` uses the ```flights``` dataset from ```nycflights13``` package to show association between departure and arrival delays. 


```{r example}
library(graphs)
library(nycflights13)

example_data <- data.frame(
  age = c(20, 22, 30, 35, 42, 50, 63, 68, 70,75, 80),
  total_lipid_count = c(120, 123, 130, 150, 175, 172, 185, 190, 200, 198, 205)
)
graphs::scatter_plot (example_data, age, total_lipid_count)

flight_delay_example <- graphs::scatter_plot(nycflights13::flights, dep_delay, arr_delay)
flight_delay_example
```

